Light and growth form interact to shape stomatal ratio among British angiosperms

### 2017-11-14 ms/ms.Rnw
finalizng ms

$^1$ Biodiversity Research Centre and Botany Department, University of British Columbia, Vancouver, British Columbia V6T 1Z4, Canada \\
\\
\textit{Author for correspondence:} \\
\textit{Christopher D. Muir} \\
\textit{Tel:} +17782284851 \\
\textit{Email:} chrisdmuir@gmail.com \\
University of British Columbia \\
6270 University Blvd. \\
Vancouver, BC, Canada \\
V6T 1Z4 \\
\\
Short title: Shedding light on stomatal evolution\\
\\
Word count: \\
Summary: 199\\
Introduction: 1355\\
Materials and Methods: 1698\\
Results: 582\\
Discussion: 1935\\
Acknowledgement: 26\\
4 Figures and 1 Table, 5 Supplemental Figures

@@

\linenumbers
\setstretch{\stretchy}
%\pagenumbering{gobble}
%\raggedright

@@

Data and annotated source code to generate this manuscript are available on GitHub (https://github.com/cdmuir/britstom) and Dryad \citep{Muir_dryad}.

@@

\bibliography{refs}
\bibliographystyle{evolution}

@@

\begin{figure}[ht]
\centerline{\includegraphics[width=0.5\textwidth]{figures/figure_SR-lf.pdf}}
%\centerline{\includegraphics[angle=270]{figures/figure_SR-lf.eps}} % Needed this to upload file to journal website
\caption{The effect of light on stomatal ratio depends on Raunki\ae r life form. Greater Ellenberg light indicator values (\el) are associated with greater stomatal ratio ($\mathrm{SR_{even}}$) in therophytes, hemicryptophytes, and chamaephytes but not geophytes and phanerophytes. The maximum likelihood slope from phylogenetic regression is given with statistical significance based on 10$^4$ parametric bootstrap samples. Numbers in parentheses next to Raunki\ae r life form are the sample sizes in the final dataset. Estimated slopes (solid line) and 95\% bootstrapped confidence intervals (gray polygon between dashed lines) are plotted against raw data. Points have been jittered for visual clarity.} 
\label{fig:SR-lf}
\end{figure}

@@

@@

\begin{figure}[ht]
\centerline{\includegraphics[width=0.5\textwidth]{figures/figure_SR-hf.pdf}}
%\centerline{\includegraphics[angle=270]{figures/figure_SR-hf.eps}} % Needed this to upload file to journal website
\caption{The effect of light on stomatal ratio depends on growth form. Greater Ellenberg light indicator values (\el) are associated with greater stomatal ratio ($\mathrm{SR_{even}}$) in annual, biennual, and perennial herbs, but not shrubs or trees. The maximum likelihood slope from phylogenetic regression is given with statistical significance based on 10$^4$ parametric bootstrap samples. Numbers in parentheses next to growth form are the sample sizes in the final dataset. Estimated slopes (solid line) and 95\% bootstrapped confidence intervals (gray polygon between dashed lines) are plotted against raw data. Points have been jittered for visual clarity.} 
\label{fig:SR-hf}
\end{figure}
\end{document}

>>>>

$^1$ Biodiversity Research Centre and Botany Department, University of British Columbia, Vancouver, British Columbia V6T 1Z4, Canada \\
\\
\textit{Twitter handle:} @thegoodphyte \\
\\
\textit{Author for correspondence:} \\
\textit{Christopher D. Muir} \\
\textit{Tel:} +17782284851 \\
\textit{Email:} chrisdmuir@gmail.com \\
University of British Columbia \\
6270 University Blvd. \\
Vancouver, BC, Canada \\
V6T 1Z4 \\
\\
Short title: Shedding light on stomatal evolution\\
\\
Word count: \\
Summary: 199\\
Introduction: 1355\\
Materials and Methods: 1698\\
Results: 582\\
Discussion: 1935\\
Acknowledgement: 26\\
4 Figures and 1 Table, 5 Supplemental Figures

@@

%\linenumbers
%\setstretch{\stretchy}
\pagenumbering{gobble}
%\raggedright

@@

Data and annotated source code to generate this manuscript are available on GitHub (https://github.com/cdmuir/britstom) and processed data files are archived on Data Dryad (https://doi.org/10.5061/dryad.5q5q6).

@@

\bibliography{refs}
\bibliographystyle{newphyt}

%--------------------------------------------------
% Supporting Figure Captions
%--------------------------------------------------

\section*{Supporting figure captions}

Figure S1: Most hydrophytes are hyperstomatous, having most stomata on the adaxial (`upper') surface

Figure S2: Raunki\ae r life form and plant habit broadly overlap.

Figure S3: Phylogenetic diversification of stomatal ratio follows growth form and light tolerance.

Figure S4: Growth forms have different tolerances for sun and shade among British angiosperms.

Figure S5: The effect of light on stomatal ratio depends on growth form.

@@

\begin{figure}[ht]
\centerline{\includegraphics[width=0.5\textwidth]{figures/figure_SR-lf.pdf}}
%\centerline{\includegraphics[angle=270]{figures/figure_SR-lf.eps}} % Needed this to upload file to journal website
\caption{The effect of light on stomatal ratio depends on Raunki\ae r life form. Greater Ellenberg light indicator values (\el) are associated with greater stomatal ratio ($\mathrm{SR_{even}}$) in therophytes, hemicryptophytes, and chamaephytes but not geophytes and phanerophytes. The maximum likelihood slope from phylogenetic regression is given with statistical significance based on 10$^4$ parametric bootstrap samples. Numbers in parentheses next to Raunki\ae r life form are the sample sizes in the final dataset. Estimated slopes (solid line) and 95\% bootstrapped confidence intervals (gray polygon between dashed lines) are plotted against raw data. Points have been jittered for visual clarity. Key to symbols: n.s. = not significant,  $^*~P < 0.05$, $^{**}~P < 0.01$, $^{***}~P < 0.001$.} 
\label{fig:SR-lf}
\end{figure}

@@

\begin{center}
{\Huge Light and growth form interact to shape stomatal ratio among British angiosperms}

{\large Christopher D. Muir}

{\large Accepted on 10 November 2017}

\end{center}

@@

\begin{figure}[ht]
\centerline{\includegraphics[width=0.5\textwidth]{figures/figure_SR-hf.pdf}}
%\centerline{\includegraphics[angle=270]{figures/figure_SR-hf.eps}} % Needed this to upload file to journal website
\caption{The effect of light on stomatal ratio depends on growth form. Greater Ellenberg light indicator values (\el) are associated with greater stomatal ratio ($\mathrm{SR_{even}}$) in annual, biennual, and perennial herbs, but not shrubs or trees. The maximum likelihood slope from phylogenetic regression is given with statistical significance based on 10$^4$ parametric bootstrap samples. Numbers in parentheses next to growth form are the sample sizes in the final dataset. Estimated slopes (solid line) and 95\% bootstrapped confidence intervals (gray polygon between dashed lines) are plotted against raw data. Points have been jittered for visual clarity. Key to symbols: n.s. = not significant,  $^*~P < 0.05$, $^{**}~P < 0.01$, $^{***}~P < 0.001$.} 
\label{fig:SR-hf}
\end{figure}
\end{document}
